The Name of the Title Is Hope

### 2024-11-09 paper/paper.tex
Added example marginal

\usepackage{mathtools}
\usepackage{multirow}

@@

Let $C \subseteq \mathcal{A}$. Let $\Omega_C = \Pi_{i \in C} \Omega_i$. The \emph{marginal}\cite{barak2007privacy,mckenna2021winning} on $C$ is a vector $\mu \in \mathbb{R}^{\abs{\Omega_C}}$, indexed by domain element $t \in \Omega_C$, such that each entry is a count $\mu_t = \Sigma_{x \in \db} \vmathbb{1} [x_C = t]$ where $\vmathbb{1}$ is the indicator function. Let $M_C(\db)$ be the function that computes the marginal on $C$, i.e., $\mu = M_C(\db)$.

@@

@@

Some examples.  A paginated journal article \cite{Abril07}

>>>>

\usepackage{mathtools}
\usepackage{multirow}
\usepackage{subcaption}

@@

Let $C \subseteq \mathcal{A}$. Let $\Omega_C = \Pi_{i \in C} \Omega_i$. The \emph{marginal}\cite{barak2007privacy,mckenna2021winning} on $C$ is a vector $\mu \in \mathbb{R}^{\abs{\Omega_C}}$, indexed by domain element $t \in \Omega_C$, such that each entry is a count $\mu_t = \Sigma_{x \in \db} \vmathbb{1} [x_C = t]$ where $\vmathbb{1}$ is the indicator function. Let $M_C(\db)$ be the function that computes the marginal on $C$, i.e., $\mu = M_C(\db)$. We call marginals of $|C| = n$ attributes $n$-way marginals.

@@

We employed the tools of the winner of the 2018 NIST Differential Privacy Synthetic Data Challenge competition\cite{NIST2018} by Ryan McKenna\cite{Ullman2022,McKenna2022,McKenna_privatePGM,mckenna2021winning,mckenna2019graphical}.

The competition considers marginals of the synthetic data. The idea of marginal-based synthetic data generation is to create a model whose marginals of samples are similar to the marginals of the original data. For example, suppose we have an original database and it's 2-way marginal on sex(Male,Female) and race(White,Black) is as shown in Table~\ref{tab:marginal-example}.

\begin{table}[h]
\caption{Example marginals.}
\label{tab:marginal-example}
\centering
\begin{subtable}[t]{0.45\linewidth}
\centering
\caption{Marginal of original data.}
\begin{tabular}{cc}
  \toprule
  Attributes & Count \\
  \midrule
  Male,White & 24 \\
  Female,White & 33 \\
  Male,Black & 13 \\
  Female,Black & 47 \\
  \bottomrule
\end{tabular}
\end{subtable}
\hspace{0.05\linewidth}
\begin{subtable}[t]{0.45\linewidth}
\centering
\caption{Marginal of synthetic data.}
\begin{tabular}{cc}
  \toprule
  Attributes & Count \\
  \midrule
  Male,White & 22 \\
  Female,White & 35 \\
  Male,Black & 10 \\
  Female,Black & 46 \\
  \bottomrule
\end{tabular}
\end{subtable}
\end{table}

@@
